---
title: "Number of crimes in different thanas of Dhaka city."
author: "Zauad Shahreer Abeer"
date: "11 August 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
	echo = FALSE,
	message = FALSE,
	warning = FALSE
)
```

```{r}
library(leaflet)

data = read.csv("./crime_data_assignment_2.csv")
data$crime_rate[data$thana == "Airport"] = round(17*100/5079,2)
data = data[order(data$total_crimes, decreasing = T),]

pal = colorNumeric("viridis", domain = data$total_crimes,
                   reverse = F)

data %>% 
  leaflet() %>%
  addTiles() %>%
  addCircleMarkers(lng = ~lon, lat = ~lat,
                   color = ~pal(total_crimes), weight = 5, 
                   radius = ~sqrt(total_crimes),
                   popup = ~paste(thana, ", total crimes:", total_crimes,
                                  ", crime rate:", crime_rate),
                   opacity = 1, fillOpacity = T,
                   fillColor = ~pal(total_crimes),
                   label = ~paste(thana, ":", total_crimes, "crimes")) %>%
  addLegend(labels = ~thana, colors = ~pal(total_crimes))
```

The higest number of crimes is observed in *Gulshan (152)*, followed by *Mohammadpur (98)*. 3rd,  4th and 5th in the list are respectively *Tejgaon (86), Dhanmondi (75) and Khilgaon (72)*.  

Among the top 5, *Gulshan, Dhanmondi and Mohammadpur* are thought to be *well-developed*. Whether crime is related to the degree of development is a reasearch topic in itself, beyond the scope of this *mini* visualization.

This work is motivated by [1](1)

***

**Reference:**

1. [Chowdhury, U., "Spatial Distribution of Street Crime Occurrences in Dhaka City", The AUST Journal of Science and Technology, Vol. 3 Num 2, July 2011](www.aust.edu/publication/articles/v3i2art2.pdf)


***


